---
title: Texas Public School Tax Levies
output: html_document
---

```{r init, echo=FALSE, message=FALSE, warning=FALSE}
source("assets/r/funcs_tables.R")
source("assets/r/libs_data.R")
path.data <- file.path('data')
```

## Description

- Summary
	- A series of `.xlsx` formatted files, provided by the Texas Comptroller, that provides tax rates, taxable values, and calculated levies for 2017-2023. _Data for additional years prior to 2017 would be helpful to conduct better analysis_.
- Sources
	- “Tax Rates and Leviers.” Texas Comptroller, [comptroller.texas.gov/taxes/property-tax/docs/2023-school-district-rates-levies.xlsx](https://comptroller.texas.gov/taxes/property-tax/docs/2023-school-district-rates-levies.xlsx). 1 Sept. 2024. 
	- “Tax Rates and Leviers.” Texas Comptroller, [comptroller.texas.gov/taxes/property-tax/docs/2022-school-district-rates-levies.xlsx](https://comptroller.texas.gov/taxes/property-tax/docs/2022-school-district-rates-levies.xlsx). 1 Sept. 2024. 
	- “Tax Rates and Leviers.” Texas Comptroller, [comptroller.texas.gov/taxes/property-tax/docs/2021-school-district-rates-levies.xlsx](https://comptroller.texas.gov/taxes/property-tax/docs/2021-school-district-rates-levies.xlsx). 1 Sept. 2024. 
	- “Tax Rates and Leviers.” Texas Comptroller, [comptroller.texas.gov/taxes/property-tax/docs/2020-school-district-rates-levies.xlsx](https://comptroller.texas.gov/taxes/property-tax/docs/2020-school-district-rates-levies.xlsx). 1 Sept. 2024. 
	- “Tax Rates and Leviers.” Texas Comptroller, [comptroller.texas.gov/taxes/property-tax/docs/2019-school-district-rates-levies.xlsx](https://comptroller.texas.gov/taxes/property-tax/docs/2019-school-district-rates-levies.xlsx). 1 Sept. 2024. 
	- “Tax Rates and Leviers.” Texas Comptroller, [comptroller.texas.gov/taxes/property-tax/docs/2018-school-district-rates-levies.xlsx](https://comptroller.texas.gov/taxes/property-tax/docs/2018-school-district-rates-levies.xlsx). 1 Sept. 2024. 
	- “Tax Rates and Leviers.” Texas Comptroller, [comptroller.texas.gov/taxes/property-tax/docs/2017-school-district-rates-levies.xlsx](https://comptroller.texas.gov/taxes/property-tax/docs/2017-school-district-rates-levies.xlsx). 1 Sept. 2024. 
- Data

```{r levies, warning=FALSE, message=FALSE, echo=FALSE, cache=TRUE, eval=TRUE}
# Read original source files
levies_2023 <- read_excel(file.path(path.data,
					  												'2023-school-district-rates-levies.xlsx')) %>%
	data.table
levies_2022 <- read_excel(file.path(path.data,
					  												'2022-school-district-rates-levies.xlsx')) %>%
	data.table
levies_2021 <- read_excel(file.path(path.data,
					  												'2021-school-district-rates-levies.xlsx')) %>%
	data.table
levies_2020 <- read_excel(file.path(path.data,
					  												'2020-school-district-rates-levies.xlsx')) %>%
	data.table
levies_2019 <- read_excel(file.path(path.data,
					  												'2019-school-district-rates-levies.xlsx')) %>%
	data.table
levies_2018 <- read_excel(file.path(path.data,
					  												'2018-school-district-rates-levies.xlsx')) %>%
	data.table
levies_2017 <- read_excel(file.path(path.data,
					  												'2017-school-district-rates-levies.xlsx')) %>%
	data.table

# Display interactive tables
print_table(levies_2023, 'ISD_tax_levies_2023')
print_table(levies_2022, 'ISD_tax_levies_2022')
print_table(levies_2021, 'ISD_tax_levies_2021')
print_table(levies_2020, 'ISD_tax_levies_2020')
print_table(levies_2019, 'ISD_tax_levies_2019')
print_table(levies_2018, 'ISD_tax_levies_2018')
print_table(levies_2017, 'ISD_tax_levies_2017')


```




