---
title: Texas Public School Finances
output: html_document
---

```{r init, echo=FALSE, message=FALSE, warning=FALSE}
source("assets/r/funcs_tables.R")
source("assets/r/libs_data.R")
path.data <- file.path('data')
```

## Description

- Summary
	- A `.xlsx` formatted file, provided by the Texas Education Agency (TEA), that provides summarized financial data from the Public Education Information Management System (PEIMS) for all Texas public schools for academic years 2007-2023.
		- **PEIMS**: "The Public Education Information Management System (PEIMS) encompasses all data requested and received by TEA about public education, including student demographic and academic performance, personnel, financial, and organizational information."^[“Public Education Information Management System.” Texas Education Agency, Texas Education Agency, 18 Aug. 2019, [tea.texas.gov/reports-and-data/data-submission/peims](https://tea.texas.gov/reports-and-data/data-submission/peims). ]
- Source
	- “PEIMS Financial Data Downloads.” PEIMS Financial Data Downloads | Texas Education Agency, Texas Education Agency, 6 May 2024, [tea.texas.gov/finance-and-grants/state-funding/state-funding-reports-and-data/peims-financial-data-downloads](https://tea.texas.gov/finance-and-grants/state-funding/state-funding-reports-and-data/peims-financial-data-downloads).

## Data

```{r finance, warning=FALSE, message=FALSE, echo=FALSE, cache=TRUE, eval=TRUE}
# Read original source file

finance_summary_2008_to_2024 <- read_excel(file.path(path.data,
                                                     '2008-2024-summarized-financial-data-03-17-2025.xlsx')) %>%
  data.table
finance_summary_2007_to_2023 <- read_excel(file.path(path.data,
                                                     '2007-2023-summarized-financial-data-0.xlsx')) %>%
  data.table
finance_summary <- rbind(finance_summary_2007_to_2023,finance_summary_2008_to_2024[YEAR==2024])
finance_summary[,`DISTRICT NUMBER`:=gsub("'","",`DISTRICT NUMBER`)]



# Display interactive table
print_table(finance_summary, 'ISD_financial_data_2007_to_2024')
```




