---
title: "FAQ: Nov 2025 Election Property Tax Measures" 
---

<script src="lib/core-js-2.5.3/shim.min.js"></script>
<script src="lib/react-18.2.0/react.min.js"></script>
<script src="lib/react-18.2.0/react-dom.min.js"></script>
<script src="lib/reactwidget-1.0.0/react-tools.js"></script>
<script src="lib/htmlwidgets-1.6.4/htmlwidgets.js"></script>
<link href="lib/reactable-0.4.4/reactable.css" rel="stylesheet"/>
<script src="lib/reactable-binding-0.4.4/reactable.js"></script>

<div class="FAQ">


<p>
    <ul>
        <li>This FAQ is intended to provide transparent and well sourced information about ballot measures in the November 2025 election that could affect a Kendall County or Boerne ISD voter's property taxes, particularly the Boerne ISD Voter-Approval Tax Rate Election (VATRE).</li>
        <li>Everything contained in this website (including text, data, analyses, visualizations, etc.) is available to download as reproducible source code from a public [GitHub repository](https://github.com/joetidwell/freidenker).</li>
        <li>This site is best viewed in a desktop browser.</li>
    </ul>
</p>


```{r plotly_hack, include = FALSE, echo=FALSE, message=FALSE, warning=FALSE}
# Both plot_ly and reactable require javascript and css libraries to be
# included in the HTML head. RMarkdown doesn't do this propoerly if the
# first use of these functions is in a loop or otehrwise nested. Loading
# These libraries and 'displaying' hidden output guarantees the correct
# libraries are included.

library(htmltools)
library(plotly)
library(reactable)
library(htmltools)
library(data.table)
source("assets/r/funcs_tables.R")
htmltools::tagList(plot_ly(x = rnorm(10), type = "histogram"))
print_table(data.table(a=1,b=2),"COW")
```



```{r init, echo=FALSE, message=FALSE, warning=FALSE}
library(readxl)
library(stringr)
library(fontawesome)
library(xml2)
library(dplyr)
library(plotly)
library(foreach)
library(RColorBrewer)
library(scales)
library(waffle)

knitr::opts_chunk$set(echo = FALSE)
knitr::opts_chunk$set(message = FALSE)
knitr::opts_chunk$set(warning = FALSE)
knitr::opts_chunk$set(cache = FALSE)


###
### Globals
###

path.data <- file.path('data')
neighbor_districts <- data.table(CDN = c("130901",  # Boerne ISD
                                         "016902",  # Blanco ISD
                                         "046902",  # Comal ISD
                                         "015915",  # Northside ISD
                                         "015910",  # North East ISD
                                         "010902",  # Bandera ISD
                                         "130902"), # Comfort ISD
							 	 `DISTRICT NAME` = toupper(c("Boerne ISD",
        							 	 					 "Blanco ISD",
        							 	 					 "Comal ISD",
        							 	 					 "Northside ISD (Bexar)",
        							 	 					 "North East ISD",
        							 	 					 "Bandera ISD",
        							 	 					 "Comfort ISD")),
							 	 `TAXING UNIT ID PREFIX` = c("130-901-02-",
							 	 							 "016-902-02-",
							 	 							 "046-902-02-",
							 	 							 "015-915-02-",
							 	 							 "015-910-02-",
							 	 							 "010-902-02-",
							 	 							 "130-902-02-"))

duplicated_districts <- data.table(`DISTRICT NAME`=toupper(c("Big Sandy ISD (Upshur)",
                                                             "Big Sandy ISD (Polk)",
                                                             "Centerville ISD (Trinity)",
                                                             "Centerville ISD (Leon)",
                                                             "Chapel Hill ISD (Titus)",
                                                             "Chapel Hill ISD (Smith)",
                                                             "Dawson ISD (Dawson)",
                                                             "Dawson ISD (Navarro)",
                                                             "Edgewood ISD (Van Zandt)",
                                                             "Edgewood ISD (Bexar)",
                                                             "Highland Park ISD (Potter)",
                                                             "Highland Park ISD (Dallas)",
                                                             "Hubbard ISD (Hill)",
                                                             "Hubbard ISD (Bowie)",
                                                             "Midway ISD (Clay)",
                                                             "Midway ISD (McLennan)",
                                                             "Northside ISD (Bexar)",
                                                             "Northside ISD (Wilbarger)",
                                                             "Valley View ISD (Hidalgo)",
                                                             "Valley View ISD (Cooke)",
                                                             "Wylie ISD (Taylor)",
                                                             "Wylie ISD (Collin)")),
                                   `CDN`=c('230901',
                                           '187901',
                                           '228904',
                                           '145902',
                                           '225906',
                                           '212909',
                                           '058902',
                                           '175904',
                                           '234903',
                                           '015905',
                                           '188903',
                                           '057911',
                                           '109905',
                                           '019913',
                                           '039905',
                                           '161903',
                                           '015915',
                                           '244905',
                                           '108916',
                                           '049903',
                                           '221912',
                                           '043914')) 

comp_size <- c('top'=12000,'bottom'=9000)
BISD_district_num = "130901"

###
### Load Data
###

# Finance Summaries
finance_summary_2008_to_2024 <- read_excel(file.path(path.data,
													 '2008-2024-summarized-financial-data-03-17-2025.xlsx')) %>%
  data.table
finance_summary_2007_to_2023 <- read_excel(file.path(path.data,
													 '2007-2023-summarized-financial-data-0.xlsx')) %>%
  data.table

# Tax Levies
levies_2024 <- read_excel(file.path(path.data,'2024-school-district-rates-levies.xlsx')) %>%
  data.table 

# Economically Disadvantaged
ecodis_2024 <- read.csv(file.path(path.data, "Economically Disadvantaged Report_Statewide_Districts_2023-2024.csv")) %>% data.table

# 2024-2025 Neighoboring District Salaries
## Compiled from https://rptsvr1.tea.texas.gov/adhocrpt/adpeb.html
staff_salaries <- read_excel(file.path(path.data,'staff_salaries_2024_2025.xlsx')) %>%
  data.table 


# TAPR Teacher Turnover Data
## 2023-2024 data hand compiled from individual pdf reports since TAPR data download didn't include 
## turnover data for that year

t_2015 <- read_excel(file.path(path.data,'TAPR_Staff_2014-15.xlsx')) %>% data.table
t_2015[,year:=2015]
t_2016 <- read_excel(file.path(path.data,'TAPR_Staff_2015-16.xlsx')) %>% data.table
t_2016[,year:=2016]
t_2017 <- read_excel(file.path(path.data,'TAPR_Staff_2016-17.xlsx')) %>% data.table
t_2017[,year:=2017]
t_2018 <- read_excel(file.path(path.data,'TAPR_Staff_2017-18.xlsx')) %>% data.table
t_2018[,year:=2018]
t_2019 <- read_excel(file.path(path.data,'TAPR_Staff_2018-19.xlsx')) %>% data.table
t_2019[,year:=2019]
t_2020 <- read_excel(file.path(path.data,'TAPR_Staff_2019-20.xlsx')) %>% data.table
t_2020[,year:=2020]
t_2021 <- read_excel(file.path(path.data,'TAPR_Staff_2020-21.xlsx')) %>% data.table
t_2021[,year:=2021]
t_2022 <- read_excel(file.path(path.data,'TAPR_Staff_2021-22.xlsx')) %>% data.table
t_2022[,year:=2022]
t_2023 <- read_excel(file.path(path.data,'TAPR_Staff_2022-23.xlsx')) %>% data.table
t_2023[,year:=2023]
t_2024 <- data.table(DISTRICT=c('130901','016902','130902','015915','015910','010902','046902'),
                     DPSTURNR=c(19.5,28.2,24.2,14.4,18.6,20,17.9),
                     year=2024)

turnover_teacher <- rbind(t_2015[,.(DISTRICT,year,DPSTURNR)],
                          t_2016[,.(DISTRICT,year,DPSTURNR)],
                          t_2017[,.(DISTRICT,year,DPSTURNR)],
                          t_2018[,.(DISTRICT,year,DPSTURNR)],
                          t_2019[,.(DISTRICT,year,DPSTURNR)],
                          t_2020[,.(DISTRICT,year,DPSTURNR)],
                          t_2021[,.(DISTRICT,year,DPSTURNR)],
                          t_2022[,.(DISTRICT,year,DPSTURNR)],
                          t_2023[,.(DISTRICT,year,DPSTURNR)],
                          t_2024[,.(DISTRICT,year,DPSTURNR)])


# Tax Rates
tax_rates <- read_excel(file.path(path.data,'school-district-adopted-tax-rates.xlsx')) %>%
    data.table



###
### Munge Data
###

# Add 2024 rates
tmp <- levies_2024[,.(`School District`=toupper(`TAXING UNIT NAME`[1]),
                      `2024-2025 M&O Tax Rate`=`M&O RATE`[1],
                      `2024-2025 I&S Tax Rate`=`I&S RATE`[1]),by=`TAXING UNIT NAME`]
setkey(tmp, `School District`)
setkey(tax_rates,`School District`)
tax_rates <- tax_rates[tmp[,.(`School District`,`2024-2025 M&O Tax Rate`,`2024-2025 I&S Tax Rate`)]]


# Create table for neighboring districts tax rates
tmp <- tax_rates[CDN %in% neighbor_districts$CDN]
years <- substr(names(tmp)[3:length(tmp)],1,4) %>% unique
BISD_neighbors_combined_tax_rate <- foreach(year=years, .combine='rbind') %do% {  
                                            cols <- grep(paste0("^",year),names(tmp),value=TRUE)
                                            tmp[,.(`Tax Year` = year, `Combined Tax Rate` = sum(.SD)), 
                                                .SD=cols, by="School District"]
}

# Remove ' from District Number
turnover_teacher[,`DISTRICT NUMBER`:=gsub("'","",DISTRICT)]
turnover_teacher[,DISTRICT:=NULL]
turnover_teacher[,TURNOVER:=DPSTURNR]
turnover_teacher[,DPSTURNR:=NULL]
turnover_teacher[,TURNOVER:=as.numeric(TURNOVER)]

# Remove whitespace from names
ecodis_2024[,District.Name:=trimws(District.Name)]
ecodis_2024[,Charter.Status:=trimws(Charter.Status)]
ecodis_2024[,County.Name:=trimws(County.Name)]

# Convert district numbers to text
ecodis_2024[,District.Number:=as.character(District.Number)]
ecodis_2024[,District.Number:=paste0(paste0(rep("0",6-nchar(District.Number)),collapse=""),District.Number,collapse=""),
            by=District.Number]

# Combine finance summary files
finance_summary <- rbind(finance_summary_2007_to_2023[YEAR==2007],finance_summary_2008_to_2024)
finance_summary[,`DISTRICT NUMBER`:=gsub("'","",`DISTRICT NUMBER`)]

# De-duplicate `DISTRICT NAME` to later join on finance_summary
for(i in 1:nrow(duplicated_districts)) {
    finance_summary[`DISTRICT NUMBER`==duplicated_districts[i]$CDN,
                    `DISTRICT NAME`:=duplicated_districts[i]$`DISTRICT NAME`]
}

# Convert tax levy data to one row per district
levies_2024 <- levies_2024[,.(`TAXING UNIT NAME`,
                              `COUNTY NAME`,
							  `TAXING UNIT ID PREFIX` = substr(`TAXING UNIT ID`,1,11),
                              `MARKET VALUE`,
                              `TAXABLE VALUE M&O`,
                              `TAXABLE VALUE I&S`,
                              `NO-NEW-REVENUE RATE`,
                              `VOTER-APPROVAL RATE`,
                              `M&O RATE`,
                              `I&S RATE`,
                              `TOTAL TAX RATE`,
                              `CALCULATED LEVY`)]
setkey(levies_2024,`MARKET VALUE`)
levies_2024 <- levies_2024[,
                           .(`TAXING UNIT NAME`=`TAXING UNIT NAME`[1],
                             `COUNTY NAME`=`COUNTY NAME`[.N],
                           	 `MARKET VALUE` = sum(`MARKET VALUE`),
                             `TAXABLE VALUE M&O` = sum(`TAXABLE VALUE M&O`),
                             `TAXABLE VALUE I&S` = sum(`TAXABLE VALUE I&S`),
                             `M&O RATE` = `M&O RATE`[1],
                             `I&S RATE` = `I&S RATE`[1],
                             `TOTAL TAX RATE` = `TOTAL TAX RATE`[1],
                             `CALCULATED LEVY` = sum(`CALCULATED LEVY`)
                             ),
                           by=.(`TAXING UNIT ID PREFIX`)]
setkey(levies_2024, `TAXING UNIT NAME`)

# De-duplicate `TAXING UNIT NAME` to later join on finance_summary
levies_2024[,`TAXING UNIT NAME`:=toupper(`TAXING UNIT NAME`)]
dup_names <- levies_2024$`TAXING UNIT NAME`[duplicated(levies_2024$`TAXING UNIT NAME`)]
levies_2024[`TAXING UNIT NAME`%in%dup_names, `TAXING UNIT NAME`:=toupper(paste(`TAXING UNIT NAME`,paste0("(",`COUNTY NAME`,")")))]

# Calculate levy per student
tmp <- finance_summary[YEAR==2024,.(`TAXING UNIT NAME`=`DISTRICT NAME`,
                                    `FALL SURVEY ENROLLMENT`)]
setkey(tmp,`TAXING UNIT NAME`)
setkey(levies_2024,`TAXING UNIT NAME`)
levies_2024 <- tmp[levies_2024]
levies_2024[,`LEVY PER STUDENT`:=`CALCULATED LEVY`/`FALL SURVEY ENROLLMENT`]


###
### Tables
###

tables <- list()

# Cost of Recapture since 2006-2007 School Year
tables[['Q12']] <- finance_summary[`DISTRICT NUMBER`==BISD_district_num,
                                   .(YEAR, `DISTRICT NAME`, `ALL FUNDS-EQUITY TRANSFERS`)]

# How does Boerne ISD’s combined tax rate compare to other districts?
tables[['Q18']] <- levies_2024[`TAXING UNIT NAME` %in% neighbor_districts$`DISTRICT NAME`,
                               .(`TAXING UNIT NAME`,
                                 `TOTAL TAX RATE`)][order(`TOTAL TAX RATE`)]

# How do Boerne ISD teacher salaries compare to neighboring districts?
tables[['Q27']] <- staff_salaries

# How do Boerne ISD administrator salaries compare to neighboring districts?
tables[['Q28']] <- staff_salaries


###
### Plots
###                                   

plots <- list()
margins <- list(l = 50, r = 50,
                b = 50, t = 50,
                pad = 20)
btns_exclude <- c('sendDataToCloud', 'autoScale2d', 'resetScale2d', 'toggleSpikelines',
                  'hoverClosestCartesian', 'hoverCompareCartesian',
                  'zoom2d','pan2d','select2d','lasso2d','zoomIn2d','zoomOut2d')



# BISD and Neighbors Tax Rates
pdata <- copy(BISD_neighbors_combined_tax_rate[`Tax Year` > 2014])
pdata <- dcast(pdata, `Tax Year` ~ `School District`, value.var = "Combined Tax Rate")
ISDs <- names(pdata)[-1]
ISDs <- c(ISDs[ISDs!="BOERNE ISD"],"BOERNE ISD")
colors <- brewer.pal(n=7,"Set1")
colors[4] <- colors[7]
colors[7] <- "#8968CD" 
colors <- data.table(ISD=ISDs,color=colors)
setkey(colors, ISD)
fig <- plot_ly(pdata,
         type = "scatter",
         mode = "lines+markers",
         height = 300
       )  %>%
  layout(title = "BISD and Neighboring District's Tax Rates 2015-2024", 
         xaxis = list(title = "Year"),
         yaxis = list(title = "Combined Tax Rate", 
                      range = c(.5,1.75), 
                      tickvals = list(.5, .75,1,1.25,1.5,1.75),
                      ticktext = list("0.5", "0.75","1.00","1.25","1.50","1.75")),
         margin=margins,
         hovermode = 'x unified') %>% 
  config(displayModeBar = TRUE,
         modeBarButtonsToRemove = btns_exclude)
for (ISD in names(pdata)[-1]) {
  fig <- add_trace(fig, 
      y = pdata[[ISD]],
      x = ~`Tax Year`,
      name = ISD,
      mode = 'lines+markers',
      line = list( width = if(ISD=="BOERNE ISD") 5 else 2,
                   color = colors[ISD]$color ),
      marker = list( size = if(ISD=="BOERNE ISD") 12 else 7,
                     color = colors[ISD]$color,
                     line = list( width = 1, color="#999") ),
      opacity = if(ISD=="BOERNE ISD") 1 else .35
    )
}
plots[['Q18']] <- fig
# tables[[4]] <- copy(pdata)


# BISD Teacher Turnover Rates 2015-2024

pdata <- turnover_teacher[`DISTRICT NUMBER`%in%neighbor_districts$CDN]
setkey(pdata, `DISTRICT NUMBER`)
setkey(neighbor_districts,CDN)
pdata <- copy(pdata[neighbor_districts][,.(year,`DISTRICT NAME`,TURNOVER)])
pdata <- dcast(pdata, year ~ `DISTRICT NAME`, value.var = "TURNOVER")
ISDs <- names(pdata)[-1]
ISDs <- c(ISDs[ISDs!="BOERNE ISD"],"BOERNE ISD")
colors <- brewer.pal(n=7,"Set1")
colors[4] <- colors[7]
colors[7] <- "#8968CD" 
colors <- data.table(ISD=ISDs,color=colors)
setkey(colors, ISD)




fig <- plot_ly(pdata,
         type = "scatter",
         mode = "lines+markers",
         height = 300
       )  %>%
  layout(title = "BISD Teacher Turnover Rate 2015-2024", 
         xaxis = list(title = "Year"),
         yaxis = list(title = "Teacher Turnover Rate (%)", 
                      range = c(0,40), 
                      tickvals = seq(5,35,by=5),
                      ticktext = as.character(seq(5,35,by=5))),
         margin=margins,
         hovermode = 'x unified') %>% 
  config(displayModeBar = TRUE,
         modeBarButtonsToRemove = btns_exclude)
fig <- add_trace(fig, 
  y = pdata[["BOERNE ISD"]],
  x = ~`year`,
  name = "BOERNE ISD",
  mode = 'lines+markers',
  line = list( width = 5,
               color = colors["BOERNE ISD"]$color),
  marker = list( size = 12 ,
                 color = colors["BOERNE ISD"]$color,
                 line = list( width = 1, color="#999") ),
  opacity = 1
)

plots[['Q32']] <- fig
tables[['Q32']] <- pdata


# BISD and Neighboring District's Teacher Turnover Rates 2015-2024


fig <- plot_ly(pdata,
         type = "scatter",
         mode = "lines+markers",
         height = 300
       )  %>%
  layout(title = "BISD and Neighboring District's Teacher Turnover Rates 2015-2024", 
         xaxis = list(title = "Year"),
         yaxis = list(title = "Teacher Turnover Rate (%)", 
                      range = c(0,40), 
                      tickvals = seq(5,35,by=5),
                      ticktext = as.character(seq(5,35,by=5))),
         margin=margins,
         hovermode = 'x unified') %>% 
  config(displayModeBar = TRUE,
         modeBarButtonsToRemove = btns_exclude)

for (ISD in names(pdata)[-1]) {
  fig <- add_trace(fig, 
      y = pdata[[ISD]],
      x = ~`year`,
      name = ISD,
      mode = 'lines+markers',
      line = list( width = if(ISD=="BOERNE ISD") 5 else 2,
                   color = colors[ISD]$color ),
      marker = list( size = if(ISD=="BOERNE ISD") 12 else 7,
                     color = colors[ISD]$color,
                     line = list( width = 1, color="#999") ),
      opacity = if(ISD=="BOERNE ISD") 1 else .35
    )
}

plots[['Q33']] <- fig
tables[['Q33']] <- pdata


###
### Data Substitutions
###

tags_source <- list()

# Cost of Recapture since 2007-2008 School Year
tags_source['{{{TOTAL_RECAPTURE}}}'] <- dollar(finance_summary[`DISTRICT NUMBER`==BISD_district_num,sum(`ALL FUNDS-EQUITY TRANSFERS`)])

# How much does Boerne ISD levy in property taxes?
tags_source['{{{TOTAL_TAX_RATE_BISD}}}'] <- paste0('$',levies_2024[`TAXING UNIT NAME`=="BOERNE ISD"]$`TOTAL TAX RATE`)
tags_source['{{{TAXABLE_VALUE_BISD}}}'] <- dollar(levies_2024[`TAXING UNIT NAME`=="BOERNE ISD"]$`TAXABLE VALUE M&O`)
tags_source['{{{2024_TAX_LEVY_BISD}}}'] <- dollar(levies_2024[`TAXING UNIT NAME`=="BOERNE ISD"]$`CALCULATED LEVY`)
tags_source['{{{2024_TAX_LEVY_PER_STUDENT_BISD}}}'] <- dollar(round(levies_2024[`TAXING UNIT NAME`=="BOERNE ISD"]$`CALCULATED LEVY`/finance_summary[`DISTRICT NUMBER`==BISD_district_num & YEAR==2024]$`FALL SURVEY ENROLLMENT`))
  
# How does Boerne ISD’s tax levy per-student compare to other districts?
tags_source['{{{2024_TAX_LEVY_PER_STUDENT_BISD}}}'] <- levies_2024[`TAXING UNIT NAME`=="BOERNE ISD"]$`LEVY PER STUDENT` %>% dollar
ecdf_levy_per_student <- ecdf(levies_2024$`LEVY PER STUDENT`)
tags_source['{{{LEVY_PER_STUDENT_PERCENTILE_BISD}}}'] <- ordinal(100*round(ecdf_levy_per_student(levies_2024[`TAXING UNIT NAME`=="BOERNE ISD"]$`LEVY PER STUDENT`),2))
ecdf_levy_per_student_comp <- ecdf(levies_2024[`FALL SURVEY ENROLLMENT` <= comp_size['top'] & `FALL SURVEY ENROLLMENT` >= comp_size['bottom']]$`LEVY PER STUDENT`)
tags_source['{{{LEVY_PER_STUDENT_PERCENTILE_BISD_COMP}}}'] <- ordinal(100*round(ecdf_levy_per_student_comp(levies_2024[`TAXING UNIT NAME`=="BOERNE ISD"]$`LEVY PER STUDENT`),2))
ecdf_levy_per_student_neighbor <- ecdf(levies_2024[`TAXING UNIT NAME` %in% neighbor_districts$`DISTRICT NAME`]$`LEVY PER STUDENT`)
tags_source['{{{LEVY_PER_STUDENT_PERCENTILE_BISD_NEIGHBOR}}}'] <- ordinal(100*round(ecdf_levy_per_student_neighbor(levies_2024[`TAXING UNIT NAME`=="BOERNE ISD"]$`LEVY PER STUDENT`),2))

dists_above <- levies_2024[`TAXING UNIT NAME` %in% neighbor_districts$`DISTRICT NAME` & `LEVY PER STUDENT` > levies_2024[`TAXING UNIT NAME`=="BOERNE ISD"]$`LEVY PER STUDENT`]$`TAXING UNIT NAME` %>% str_to_title
dists_below <- levies_2024[`TAXING UNIT NAME` %in% neighbor_districts$`DISTRICT NAME` & `LEVY PER STUDENT` < levies_2024[`TAXING UNIT NAME`=="BOERNE ISD"]$`LEVY PER STUDENT`]$`TAXING UNIT NAME` %>% str_to_title
dists_above <- gsub("Isd","ISD",dists_above)
dists_below <- gsub("Isd","ISD",dists_below)
tags_source['{{{LEVY_NEIGHBOR_HIGHER}}}'] <- paste(dists_below, collapse=", ")
tags_source['{{{LEVY_NEIGHBOR_LOWER}}}'] <- paste(dists_above, collapse=", ")

# How does Boerne ISD’s combined tax rate compare to other districts?
ecdf_tax_rate <- ecdf(levies_2024$`TOTAL TAX RATE`)
tags_source['{{{TAX_RATE_PERCENTILE_BISD}}}'] <- ordinal(100*round(ecdf_tax_rate(levies_2024[`TAXING UNIT NAME`=="BOERNE ISD"]$`TOTAL TAX RATE`),2))
ecdf_tax_rate_comp <- ecdf(levies_2024[`FALL SURVEY ENROLLMENT` <= comp_size['top'] & `FALL SURVEY ENROLLMENT` >= comp_size['bottom']]$`TOTAL TAX RATE`)
tags_source['{{{TAX_RATE_PERCENTILE_BISD_COMP}}}'] <- ordinal(100*round(ecdf_tax_rate_comp(levies_2024[`TAXING UNIT NAME`=="BOERNE ISD"]$`TOTAL TAX RATE`),2))
ecdf_tax_rate_neighbor <- ecdf(levies_2024[`TAXING UNIT NAME` %in% neighbor_districts$`DISTRICT NAME`]$`TOTAL TAX RATE`)
tags_source['{{{TAX_RATE_PERCENTILE_BISD_NEIGHBOR}}}'] <- ordinal(100*round(ecdf_tax_rate_neighbor(levies_2024[`TAXING UNIT NAME`=="BOERNE ISD"]$`TOTAL TAX RATE`),2))

dists_below <- levies_2024[`TAXING UNIT NAME` %in% neighbor_districts$`DISTRICT NAME` & `TOTAL TAX RATE` > levies_2024[`TAXING UNIT NAME`=="BOERNE ISD"]$`TOTAL TAX RATE`]$`TAXING UNIT NAME` %>% str_to_title
dists_above <- levies_2024[`TAXING UNIT NAME` %in% neighbor_districts$`DISTRICT NAME` & `TOTAL TAX RATE` < levies_2024[`TAXING UNIT NAME`=="BOERNE ISD"]$`TOTAL TAX RATE`]$`TAXING UNIT NAME` %>% str_to_title
dists_above <- gsub("Isd","ISD",dists_above)
dists_below <- gsub("Isd","ISD",dists_below)
tags_source['{{{TAX_RATE_NEIGHBOR_HIGHER}}}'] <- paste(dists_below, collapse=", ")
tags_source['{{{TAX_RATE_NEIGHBOR_LOWER}}}'] <- paste(dists_above, collapse=", ")

# How does the state's funding method affect Boerne ISD?
ecdf_wealth <- ecdf(levies_2024$`TAXABLE VALUE M&O`/levies_2024$`FALL SURVEY ENROLLMENT`)
tags_source['{{{WEALTH_PER_STUDENT_BISD}}}'] <- dollar(round(levies_2024[`TAXING UNIT NAME`=="BOERNE ISD"]$`TAXABLE VALUE M&O`/levies_2024[`TAXING UNIT NAME`=="BOERNE ISD"]$`FALL SURVEY ENROLLMENT`))
tags_source['{{{WEALTH_PER_STUDENT_EISD}}}'] <- dollar(round(levies_2024[`TAXING UNIT NAME`=="EDGEWOOD ISD (BEXAR)"]$`TAXABLE VALUE M&O`/levies_2024[`TAXING UNIT NAME`=="EDGEWOOD ISD (BEXAR)"]$`FALL SURVEY ENROLLMENT`))
tags_source['{{{WEALTH_PERCENTILE_BISD_COMP}}}'] <- ordinal(100*round(ecdf_wealth(levies_2024[`TAXING UNIT NAME`=="BOERNE ISD"]$`TAXABLE VALUE M&O`/levies_2024[`TAXING UNIT NAME`=="BOERNE ISD"]$`FALL SURVEY ENROLLMENT`), 2))
tags_source['{{{WEALTH_PERCENTILE_EISD_COMP}}}'] <- ordinal(100*round(ecdf_wealth(levies_2024[`TAXING UNIT NAME`=="EDGEWOOD ISD (BEXAR)"]$`TAXABLE VALUE M&O`/levies_2024[`TAXING UNIT NAME`=="EDGEWOOD ISD (BEXAR)"]$`FALL SURVEY ENROLLMENT`), 2))

ecdf_enrollment <- ecdf(finance_summary[YEAR==2024]$`FALL SURVEY ENROLLMENT`)
tags_source['{{{1000_ENROLLMENT_PERCENTILE}}}'] <- round(ecdf_enrollment(1000)*100)
tags_source['{{{ENROLLMENT_CISD}}}'] <- levies_2024[`TAXING UNIT NAME`=="COMFORT ISD"]$`FALL SURVEY ENROLLMENT` %>% comma
tags_source['{{{ENROLLMENT_BISD}}}'] <- levies_2024[`TAXING UNIT NAME`=="BOERNE ISD"]$`FALL SURVEY ENROLLMENT` %>% comma
tags_source['{{{ENROLLMENT_NISD}}}'] <- levies_2024[`TAXING UNIT NAME`=="NORTHSIDE ISD (BEXAR)"]$`FALL SURVEY ENROLLMENT` %>% comma
tags_source['{{{ENROLLMENT_PERCENTILE_CISD_COMP}}}'] <- ordinal(100*round(ecdf_enrollment(finance_summary[YEAR==2024 & `DISTRICT NAME`=="COMFORT ISD"]$`FALL SURVEY ENROLLMENT`), 2))
tags_source['{{{ENROLLMENT_PERCENTILE_BISD_COMP}}}'] <- ordinal(100*round(ecdf_enrollment(finance_summary[YEAR==2024 & `DISTRICT NAME`=="BOERNE ISD"]$`FALL SURVEY ENROLLMENT`), 2))
tags_source['{{{ENROLLMENT_PERCENTILE_NISD_COMP}}}'] <- ordinal(100*round(ecdf_enrollment(finance_summary[YEAR==2024 & `DISTRICT NAME`=="NORTHSIDE ISD (BEXAR)"]$`FALL SURVEY ENROLLMENT`), 2))


ecdf_ecodis <- ecdf(100-ecodis_2024[Not.Economically.Disadvantaged.Percent!=-999]$Not.Economically.Disadvantaged.Percent)
tags_source['{{{ECODIS_PERCENTILE_BISD_COMP}}}'] <- ordinal(100*round(ecdf_ecodis(100-ecodis_2024[District.Name=="BOERNE ISD"]$Not.Economically.Disadvantaged.Percent), 2))
tags_source['{{{ECODIS_PERCENTILE_EISD_COMP}}}'] <- ordinal(100*round(ecdf_ecodis(100-ecodis_2024[District.Name=="EDGEWOOD ISD" & County.Name=="BEXAR COUNTY"]$Not.Economically.Disadvantaged.Percent), 2))
tags_source['{{{ECODIS_PERCENTILE_CISD_COMP}}}'] <- ordinal(100*round(ecdf_ecodis(100-ecodis_2024[District.Name=="COMFORT ISD"]$Not.Economically.Disadvantaged.Percent), 2))
tags_source['{{{ECODIS_PERCENT_EISD}}}'] <- 100-ecodis_2024[District.Name=="EDGEWOOD ISD" & County.Name=="BEXAR COUNTY"]$Not.Economically.Disadvantaged.Percent %>% round
tags_source['{{{ECODIS_PERCENT_BISD}}}'] <- 100-ecodis_2024[District.Name=="BOERNE ISD"]$Not.Economically.Disadvantaged.Percent %>% round
tags_source['{{{ECODIS_PERCENT_CISD}}}'] <- 100-ecodis_2024[District.Name=="COMFORT ISD"]$Not.Economically.Disadvantaged.Percent %>% round


# Is Boerne ISD one of the lowest funded school districts per-student in Texas?
ecodis_comp_districts <- ecodis_2024[Not.Economically.Disadvantaged.Percent > 70 &
                                     Not.Economically.Disadvantaged.Percent < 90]$District.Name
ecdf_funding_per_student <- ecdf(finance_summary[YEAR==2024]$`GEN FUNDS-TOTAL OPERATING REVENUE`/finance_summary[YEAR==2024]$`FALL SURVEY ENROLLMENT`)
ecdf_funding_per_student_pop <- ecdf(finance_summary[YEAR==2024 & 
                                                     `FALL SURVEY ENROLLMENT` > comp_size['bottom'] &
                                                     `FALL SURVEY ENROLLMENT` < comp_size['top'],
                                                     `GEN FUNDS-TOTAL OPERATING REVENUE`/`FALL SURVEY ENROLLMENT`])
ecdf_funding_per_student_ecodis <- ecdf(finance_summary[YEAR==2024 & 
                                                        `DISTRICT NAME` %in% ecodis_comp_districts,
                                                        `GEN FUNDS-TOTAL OPERATING REVENUE`/`FALL SURVEY ENROLLMENT`])
ecdf_funding_per_student_ecodis_and_pop <- ecdf(finance_summary[YEAR==2024 & 
                                                                `FALL SURVEY ENROLLMENT` > comp_size['bottom'] &
                                                                `FALL SURVEY ENROLLMENT` < comp_size['top'] &
                                                                `DISTRICT NAME` %in% ecodis_comp_districts,
                                                                `GEN FUNDS-TOTAL OPERATING REVENUE`/`FALL SURVEY ENROLLMENT`])
tags_source['{{{FUNDING_PERCENTILE_BISD_COMP}}}'] <- ordinal(round(100*ecdf_funding_per_student(finance_summary[YEAR==2024 & `DISTRICT NAME` == "BOERNE ISD",`GEN FUNDS-TOTAL OPERATING REVENUE`/`FALL SURVEY ENROLLMENT`]),2))
tags_source['{{{FUNDING_PERCENTILE_BISD_COMP_POP}}}'] <- ordinal(round(100*ecdf_funding_per_student_pop(finance_summary[YEAR==2024 & `DISTRICT NAME` == "BOERNE ISD",`GEN FUNDS-TOTAL OPERATING REVENUE`/`FALL SURVEY ENROLLMENT`]),2))
tags_source['{{{FUNDING_PERCENTILE_BISD_COMP_ECODIS}}}'] <- ordinal(round(100*ecdf_funding_per_student_ecodis(finance_summary[YEAR==2024 & `DISTRICT NAME` == "BOERNE ISD",`GEN FUNDS-TOTAL OPERATING REVENUE`/`FALL SURVEY ENROLLMENT`]),2))
tags_source['{{{FUNDING_PERCENTILE_BISD_COMP_ECODIS_AND_POP}}}'] <- ordinal(round(100*ecdf_funding_per_student_ecodis_and_pop(finance_summary[YEAR==2024 & `DISTRICT NAME` == "BOERNE ISD",`GEN FUNDS-TOTAL OPERATING REVENUE`/`FALL SURVEY ENROLLMENT`]),2))

#Compared to all districts in the state, how do districts neighboring Boerne ISD rank in per-student funding?
tags_source['{{{FUNDING_PERCENTILE_BANDERA_COMP}}}'] <- ordinal(round(100*ecdf_funding_per_student(finance_summary[YEAR==2024 & `DISTRICT NAME` == "BANDERA ISD",`GEN FUNDS-TOTAL OPERATING REVENUE`/`FALL SURVEY ENROLLMENT`]),2))   
tags_source['{{{FUNDING_PERCENTILE_BLANCO_COMP}}}'] <- ordinal(round(100*ecdf_funding_per_student(finance_summary[YEAR==2024 & `DISTRICT NAME` == "BLANCO ISD",`GEN FUNDS-TOTAL OPERATING REVENUE`/`FALL SURVEY ENROLLMENT`]),2))   
tags_source['{{{FUNDING_PERCENTILE_COMAL_COMP}}}'] <- ordinal(round(100*ecdf_funding_per_student(finance_summary[YEAR==2024 & `DISTRICT NAME` == "COMAL ISD",`GEN FUNDS-TOTAL OPERATING REVENUE`/`FALL SURVEY ENROLLMENT`]),2))   
tags_source['{{{FUNDING_PERCENTILE_COMFORT_COMP}}}'] <- ordinal(round(100*ecdf_funding_per_student(finance_summary[YEAR==2024 & `DISTRICT NAME` == "COMFORT ISD",`GEN FUNDS-TOTAL OPERATING REVENUE`/`FALL SURVEY ENROLLMENT`]),2))   
tags_source['{{{FUNDING_PERCENTILE_NORTHEAST_COMP}}}'] <- ordinal(round(100*ecdf_funding_per_student(finance_summary[YEAR==2024 & `DISTRICT NAME` == "NORTH EAST ISD",`GEN FUNDS-TOTAL OPERATING REVENUE`/`FALL SURVEY ENROLLMENT`]),2))   
tags_source['{{{FUNDING_PERCENTILE_NORTHSIDE_COMP}}}'] <- ordinal(round(100*ecdf_funding_per_student(finance_summary[YEAR==2024 & `DISTRICT NAME` == "NORTHSIDE ISD (BEXAR)",`GEN FUNDS-TOTAL OPERATING REVENUE`/`FALL SURVEY ENROLLMENT`]),2))   

#If Boerne ISD had the estimated tax revenue from the proposed VATRE in 2024, how would its relative per-student funding have changed?
tags_source['{{{FUNDING_PERCENTILE_BISD_COMP_COUNTERFACTUAL_2024}}}'] <- ordinal(round(100*ecdf_funding_per_student(finance_summary[YEAR==2024 & `DISTRICT NAME` == "BOERNE ISD",(`GEN FUNDS-TOTAL OPERATING REVENUE`+4800000)/`FALL SURVEY ENROLLMENT`]),2))

# What would Boerne ISD’s tax rate have to be to obtain per student funding comparable to a smaller neighboring district like Comfort ISD?
copper_penny_yield_2024 <- 49.28
cisd_rev_per_student <- finance_summary[YEAR==2024 & `DISTRICT NAME`=="COMFORT ISD",`GEN FUNDS-TOTAL OPERATING REVENUE`/`FALL SURVEY ENROLLMENT`]
bisd_rev_per_student <- finance_summary[YEAR==2024 & `DISTRICT NAME`=="BOERNE ISD",`GEN FUNDS-TOTAL OPERATING REVENUE`/`FALL SURVEY ENROLLMENT`]
bisd_2024_enrollment <- finance_summary[YEAR==2024 & `DISTRICT NAME`=="BOERNE ISD"]$`FALL SURVEY ENROLLMENT`
bisd_additional_required_revenue <- (cisd_rev_per_student - bisd_rev_per_student)*bisd_2024_enrollment
bisd_additional_tax_rate <- bisd_additional_required_revenue/(copper_penny_yield_2024 * bisd_2024_enrollment)

tags_source['{{{GF_REVENUE_PER_STUDENT_BISD}}}'] <- dollar(bisd_rev_per_student)
tags_source['{{{GF_REVENUE_PER_STUDENT_CISD}}}'] <- dollar(cisd_rev_per_student)
tags_source['{{{BISD_TAX_INCREASE_CISD}}}'] <- dollar(bisd_additional_tax_rate/100)
tags_source['{{{BISD_2024_TAX_RATE}}}'] <- levies_2024[`TAXING UNIT NAME`=="BOERNE ISD"]$`TOTAL TAX RATE`
tags_source['{{{BISD_2024_CISD_COMP_TAX_RATE}}}'] <- dollar(levies_2024[`TAXING UNIT NAME`=="BOERNE ISD"]$`TOTAL TAX RATE` + bisd_additional_tax_rate/100)

# What does Boerne ISD spend money on?
tags_source['{{{TOTAL_PAYROLL_BISD}}}'] <- dollar(finance_summary[YEAR==2024 & `DISTRICT NAME`=="BOERNE ISD"]$`GEN FUNDS-TOTAL PAYROLL EXPENDITURES`)
tags_source['{{{GEN_FUNDS_OP_REVENUE_BISD}}}'] <- dollar(finance_summary[YEAR==2024 & `DISTRICT NAME`=="BOERNE ISD"]$`GEN FUNDS-TOTAL OPERATING REVENUE`)
tags_source['{{{PAYROLL_PERCENT_BISD}}}'] <- round(finance_summary[YEAR==2024 & `DISTRICT NAME`=="BOERNE ISD", `GEN FUNDS-TOTAL PAYROLL EXPENDITURES`/`GEN FUNDS-TOTAL OPERATING REVENUE`]*100)

# How do Boerne ISD teacher salaries compare to neighboring districts?
tags_source['{{{SALARY_TEACHER_BOERNEISD}}}'] <- dollar(staff_salaries[`District Name`=="BOERNE ISD"]$Teachers)
tags_source['{{{SALARY_TEACHER_BOERNEISD_DELTA}}}'] <- dollar(round(mean(staff_salaries$Teachers) - staff_salaries[`District Name`=="BOERNE ISD"]$Teachers)) 
tmp <- gsub(" ISD","",staff_salaries[Teachers < staff_salaries[`District Name`=="BOERNE ISD"]$Teachers]$`District Name`) %>% str_to_title
tags_source['{{{SALARY_TEACHER_HIGHER}}}'] <- knitr::combine_words(tmp)
tmp <- gsub(" ISD","",staff_salaries[Teachers > staff_salaries[`District Name`=="BOERNE ISD"]$Teachers]$`District Name`) %>% str_to_title
tags_source['{{{SALARY_TEACHER_LOWER}}}'] <- knitr::combine_words(tmp)

# How do Boerne ISD administrator salaries compare to neighboring districts?
tags_source['{{{SALARY_ADMINISTRATOR_BOERNEISD}}}'] <- dollar(staff_salaries[`District Name`=="BOERNE ISD"]$`All Administrators`)
tags_source['{{{SALARY_ADMINISTRATOR_BOERNEISD_DELTA}}}'] <- dollar(round(mean(staff_salaries$`All Administrators`) - staff_salaries[`District Name`=="BOERNE ISD"]$`All Administrators`)) 
tmp <- gsub(" ISD","",staff_salaries[`All Administrators` < staff_salaries[`District Name`=="BOERNE ISD"]$`All Administrators`]$`District Name`) %>% str_to_title
tags_source['{{{SALARY_ADMINISTRATOR_HIGHER}}}'] <- knitr::combine_words(tmp)
tmp <- gsub(" ISD","",staff_salaries[`All Administrators` > staff_salaries[`District Name`=="BOERNE ISD"]$`All Administrators`]$`District Name`) %>% str_to_title
tags_source['{{{SALARY_ADMINISTRATOR_LOWER}}}'] <- knitr::combine_words(tmp)

tags_source['{{{SALARY_PRINCIPAL_BOERNEISD}}}'] <- dollar(staff_salaries[`District Name`=="BOERNE ISD"]$Principals)
tags_source['{{{SALARY_PRINCIPAL_BOERNEISD_DELTA}}}'] <- dollar(-1*round(mean(staff_salaries$Principals) - staff_salaries[`District Name`=="BOERNE ISD"]$Principals)) 
tmp <- gsub(" ISD","",staff_salaries[Principals < staff_salaries[`District Name`=="BOERNE ISD"]$Principals]$`District Name`) %>% str_to_title
tags_source['{{{SALARY_PRINCIPAL_HIGHER}}}'] <- knitr::combine_words(tmp)
tmp <- gsub(" ISD","",staff_salaries[Principals > staff_salaries[`District Name`=="BOERNE ISD"]$Principals]$`District Name`) %>% str_to_title
tags_source['{{{SALARY_PRINCIPAL_LOWER}}}'] <- knitr::combine_words(tmp)

tags_source['{{{SALARY_ASSISTANT_PRINCIPAL_BOERNEISD}}}'] <- dollar(staff_salaries[`District Name`=="BOERNE ISD"]$`Assistant Principals`)
tags_source['{{{SALARY_ASSISTANT_PRINCIPAL_BOERNEISD_DELTA}}}'] <- dollar(-1*round(mean(staff_salaries$`Assistant Principals`) - staff_salaries[`District Name`=="BOERNE ISD"]$`Assistant Principals`)) 
tmp <- gsub(" ISD","",staff_salaries[`Assistant Principals` < staff_salaries[`District Name`=="BOERNE ISD"]$`Assistant Principals`]$`District Name`) %>% str_to_title
tags_source['{{{SALARY_ASSISTANT_PRINCIPAL_HIGHER}}}'] <- knitr::combine_words(tmp)
tmp <- gsub(" ISD","",staff_salaries[`Assistant Principals` > staff_salaries[`District Name`=="BOERNE ISD"]$`Assistant Principals`]$`District Name`) %>% str_to_title
tags_source['{{{SALARY_ASSISTANT_PRINCIPAL_LOWER}}}'] <- knitr::combine_words(tmp)

tags_source['{{{SALARY_SUPERINTENDENT_BOERNEISD}}}'] <- dollar(staff_salaries[`District Name`=="BOERNE ISD"]$Superintendent)
tags_source['{{{SALARY_SUPERINTENDENT_BOERNEISD_DELTA}}}'] <- dollar(round(mean(staff_salaries$Superintendent) - staff_salaries[`District Name`=="BOERNE ISD"]$Superintendent)) 
tmp <- gsub(" ISD","",staff_salaries[Superintendent < staff_salaries[`District Name`=="BOERNE ISD"]$Superintendent]$`District Name`) %>% str_to_title
tags_source['{{{SALARY_SUPERINTENDENT_HIGHER}}}'] <- knitr::combine_words(tmp)
tmp <- gsub(" ISD","",staff_salaries[Superintendent > staff_salaries[`District Name`=="BOERNE ISD"]$Superintendent]$`District Name`) %>% str_to_title
tags_source['{{{SALARY_SUPERINTENDENT_LOWER}}}'] <- knitr::combine_words(tmp)


# How has Boerne ISD's teacher turnover rate changed in the last 10 years?

tags_source['{{{BISD_TURNOVER_2016_2023}}}'] <- round(turnover_teacher[`DISTRICT NUMBER`=="130901" &
                                                                       year %in% seq(2016,2023),
                                                                       mean(TURNOVER)],1)
tags_source['{{{BISD_TURNOVER_2015}}}'] <- round(turnover_teacher[`DISTRICT NUMBER`=="130901" &
                                                                       year == 2015,
                                                                       TURNOVER],1)
tags_source['{{{BISD_TURNOVER_2024}}}'] <- round(turnover_teacher[`DISTRICT NUMBER`=="130901" &
                                                                       year == 2024,
                                                                       TURNOVER],1)




# BISD and Neighboring District's Teacher Turnover Rates 2015-2024

neighbor_turnover <- turnover_teacher[`DISTRICT NUMBER`%in%neighbor_districts$CDN]
setkey(neighbor_turnover, `DISTRICT NUMBER`)
setkey(neighbor_districts,CDN)
neighbor_turnover <- copy(neighbor_turnover[neighbor_districts][,.(year,`DISTRICT NAME`,TURNOVER)])
tmp <- neighbor_turnover[,.(`DISTRICT NAME`,rank(TURNOVER)),by=year]
tags_source['{{{TURNOVER_TEACHER_HIGHER}}}'] <- knitr::combine_words(str_to_title(gsub(" ISD","",tmp[year==2024 & V2 < tmp[year==2024 & `DISTRICT NAME`=="BOERNE ISD"]$V2]$`DISTRICT NAME`)))
tags_source['{{{TURNOVER_TEACHER_LOWER}}}'] <- knitr::combine_words(str_to_title(gsub(" ISD","",tmp[year==2024 & V2 > tmp[year==2024 & `DISTRICT NAME`=="BOERNE ISD"]$V2]$`DISTRICT NAME`)))



# finance_summary[YEAR==2024 & `DISTRICT NAME`=="LAKE TRAVIS ISD"]


# ecodis_comp_districts[!(District.Name %in% finance_summary[YEAR==2024]$`DISTRICT NAME`)]

# sort(unique(finance_summary$`DISTRICT NAME`))

# n.under.9000 <- finance_summary[YEAR==2024 & `FALL SURVEY ENROLLMENT` < 9000,.N]
# n.over.12000 <- finance_summary[YEAR==2024 & `FALL SURVEY ENROLLMENT` > 12000,.N]
# n.total <- finance_summary[YEAR==2024,.N]
# n.under.1000 <- finance_summary[YEAR==2024 & `FALL SURVEY ENROLLMENT` < 1000,.N]

# CDN_comp_size <- finance_summary[YEAR==2024 & 
#                                  `FALL SURVEY ENROLLMENT` > comp_size['bottom'] &
#                                  `FALL SURVEY ENROLLMENT` < comp_size['top'] ]$`DISTRICT NUMBER`

# CDN_comp_ecodis <- ecodis_2024[Not.Economically.Disadvantaged.Percent > 70 &
#                                Not.Economically.Disadvantaged.Percent < 90 &
#                                Charter.Status == "TRADITIONAL ISD/CSD"]$District.Number


# ecodis_2024[District.Name=="BOERNE ISD"]

# BISD_district_num %in% CDN_comp_ecodis

# comp_districts <- finance_summary[YEAR==2024 & 
#                                   `DISTRICT NUMBER` %in% intersect(CDN_comp_size,CDN_comp_ecodis),
#                                   .(`DISTRICT NUMBER`,
#                                     `DISTRICT NAME`,
#                                     `FALL SURVEY ENROLLMENT`,
#                                     `ALL FUNDS-TOTAL OPERATING REVENUE`,
#                                     `GEN FUNDS-TOTAL OPERATING REVENUE`,
#                                     `GEN FUNDS-TOTAL DISBURSEMENTS`,
#                                     `ALL FUNDS-TOTAL DISBURSEMENTS`)]
# comp_districts[,`GF PER STUDENT`:=`GEN FUNDS-TOTAL OPERATING REVENUE`/`FALL SURVEY ENROLLMENT`]
# comp_districts[order(`GF PER STUDENT`)][1:10]


# ecdf_funding <- ecdf(comp_districts$`GF PER STUDENT`)
# ecdf_funding(comp_districts[`DISTRICT NUMBER`==BISD_district_num]$`GF PER STUDENT`)



# ecodis_2024$Charter.Status



# tmp <- levies_2024[`TAXING UNIT NAME` %in% unique(finance_summary[`DISTRICT NUMBER` %in% CDN_comp_ecodis]$`DISTRICT NAME`)]
# ecdf(tmp$`LEVY PER STUDENT`)(tmp[`TAXING UNIT NAME`=="BOERNE ISD"]$`LEVY PER STUDENT`)

# tmp[,quantile(`FALL SURVEY ENROLLMENT`,na.rm=TRUE)]

# comp_districts <- finance_summary[YEAR==2024 & 
#                                   `FALL SURVEY ENROLLMENT` > 8000 &
#                                   `FALL SURVEY ENROLLMENT` < 13000 ,
#                                   .(`DISTRICT NUMBER`,
#                                     `DISTRICT NAME`,
#                                     `FALL SURVEY ENROLLMENT`,
#                                     `ALL FUNDS-TOTAL OPERATING REVENUE`,
#                                     `GEN FUNDS-TOTAL OPERATING REVENUE`,
#                                     `GEN FUNDS-TOTAL DISBURSEMENTS`,
#                                     `ALL FUNDS-TOTAL DISBURSEMENTS`)]


# a <- finance_summary[`DISTRICT NAME`=="DIVIDE ISD" & YEAR==2024]$`FALL SURVEY ENROLLMENT`
# b <- finance_summary[`DISTRICT NAME`=="DIVIDE ISD" & YEAR==2024]$`ALL FUNDS-TOTAL OPERATING REVENUE`
# dollar(b/a)
# a <- finance_summary[`DISTRICT NAME`=="CENTER POINT ISD" & YEAR==2024]$`FALL SURVEY ENROLLMENT`
# b <- finance_summary[`DISTRICT NAME`=="CENTER POINT ISD" & YEAR==2024]$`ALL FUNDS-TOTAL OPERATING REVENUE`
# dollar(b/a)
# a <- finance_summary[`DISTRICT NAME`=="COMFORT ISD" & YEAR==2024]$`FALL SURVEY ENROLLMENT`
# b <- finance_summary[`DISTRICT NAME`=="COMFORT ISD" & YEAR==2024]$`ALL FUNDS-TOTAL OPERATING REVENUE`
# dollar(b/a)
# a <- finance_summary[`DISTRICT NAME`=="BOERNE ISD" & YEAR==2024]$`FALL SURVEY ENROLLMENT`
# b <- finance_summary[`DISTRICT NAME`=="BOERNE ISD" & YEAR==2024]$`ALL FUNDS-TOTAL OPERATING REVENUE`
# dollar(b/a)




# finance_summary[`DISTRICT NAME`=="WESTLAKE ACADEMY CHARTER SCHOOL"]

# names(ecodis_2024)
# trimws(ecodis_2024$District.Name)
# ecdf_ecodis <- ecdf(ecodis_2024$Not.Economically.Disadvantaged.Percent)
# ecodis_2024[District.Name=="BOERNE ISD"]$Not.Economically.Disadvantaged.Percent

###
### Load Questions
###

# Load qs
BISD_VATRE_questions <- as_list(read_xml(file.path(path.data,"FAQ_BoerneISD_VATRE.xml")))[[1]]
BISD_VATRE_questions <- lapply(BISD_VATRE_questions, function(x) unlist(x))
names(BISD_VATRE_questions) <- paste0("Q",1:length(BISD_VATRE_questions))


###
### Substitute Tags
###

for (i in 1:length(BISD_VATRE_questions)) {

	tags_dest <- unlist(str_extract_all(BISD_VATRE_questions[[i]]['answer'], 
									  "(\\{\\{\\{\\w+\\}\\}\\})", 
									  simplify=FALSE))
	if (length(tags_dest)>0) {
		for (t in tags_dest) {
			BISD_VATRE_questions[[i]]['answer'] <- gsub(t,
	  												    tags_source[t],
												        BISD_VATRE_questions[[i]]['answer'],
												        fixed=TRUE)
		}	
	}

    tags_dest <- unlist(str_extract_all(BISD_VATRE_questions[[i]]['details'], 
                                      "(\\{\\{\\{\\w+\\}\\}\\})", 
                                      simplify=FALSE))
    if (length(tags_dest)>0) {
        for (t in tags_dest) {
            BISD_VATRE_questions[[i]]['details'] <- gsub(t,
                                                        tags_source[t],
                                                        BISD_VATRE_questions[[i]]['details'],
                                                        fixed=TRUE)
        }   
    }


}


display_plot <- function(p) {
	paste(
		'<div style="padding: 30px;">',
		htmltools::tagList(p),
		'</div>'
	)
}

display_question <- function(q,id,tabwidth=800,rows=10) {
	out <- paste(
        # paste0('<span id="',id,'_start" style="scroll-margin-top: 100px;"></span>'),
		paste0('<h3 id="',id,'_start" style="scroll-margin-top: 100px;">',id,': ',q['title'],'</h3>'),
		'<div class="answer_wrapper">',
		trimws(gsub('\\s+', ' ', q['answer'])),
		ifelse(is.null(plots[[id]]), '', display_plot(plots[[id]])),
		sep = "\n"
	)
	if(!(is.na(q['details']))) {
		out <- paste(out,
			'<p style="margin-top: 5px;">',
			paste0('<a class="collapsed" data-toggle="collapse" href="#',id,'">'),
			'<span class="if-collapsed">Show Details</span>',
			'<span class="if-not-collapsed">Hide Details</span>',
			'</a>',
			'</p>',
			paste0('<div class="collapse" id="',id,'">'),
			'<div class="card card-body answer-details">',
	    	trimws(gsub('\\s+', ' ', q['details'])),
			ifelse(is.null(tables[[id]]),'',print_table_html(tables[[id]], paste0("table_", id, sep=""), width=tabwidth, pagesize=rows)),
			'</div>',
			'</div>',
			sep = "\n"			
		)
	}

	out <- paste(out, '</div><br/>', sep = "\n")

	cat(out)
}





```


```{r plots}

```


```{r, results='asis'}

topic <- ''
i <- 0

for(q in BISD_VATRE_questions) {
    i <- i + 1
    if(q['topic'] != topic) {
        topic <- q['topic']
        cat('<h2>')
        cat(topic)
        cat('</h2>')
    }
    cat('<a href="#',paste0("Q",i),'_start"><h4>',paste0("Q",i),': ',q['title'],'</h4></a>',sep="")
}
cat('<hr/>')


topic <- ''
i <- 0

for(q in BISD_VATRE_questions) {
	i <- i + 1
  	if(q['topic'] != topic) {
  		topic <- q['topic']
  		cat('<h1>')
  		cat(topic)
  		cat('</h1><hr/>')
  	}
  	display_question(q, paste0("Q",i))
}




# for(q in BISD_VATRE_questions) {
# 	i <- i + 1
# 	if(is.null(figures[[i]]) & is.null(tables[[i]])) {
# 		display_question(q, paste0("Q",i))
# 	} else if (!is.null(figures[[i]]) & is.null(tables[[i]])) {
# 		display_question(q, paste0("Q",i),p=figures[[i]])
# 	} else if (is.null(figures[[i]]) & !is.null(tables[[i]])) {
# 		display_question(q, paste0("Q",i),tab=tables[[i]],rows=nrow(tables[[i]]))
# 	} else {
# 		display_question(q, paste0("Q",i),p=figures[[i]],tab=tables[[i]],rows=nrow(tables[[i]]))
# 	}
# }

```


</div>